Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-08-17 nir_companions.tex
Add JWST citation

\subsection{Future implementation}
\label{subsec:future}
\subsubsection{High resolution instrumentation}
\label{subsubsec:highres}
The future of high resolution near- and mid- IR spectrographs is looking bright, with many new ground- and space-based instruments currently being developed. Notable examples include CARMENES (550--1710~nm, R=82\,000) which is now operational~\citep{quirrenbach_carmenes_2014}, while SPIRou (980--2350~nm, R=73\,500)~\citep{artigau_spirou_2014} and NIRPS (970--1810~nm, R=100\,000)~\citep{bouchy_nearinfrared_2017} are still being assembled and installed. The eagerly awaited \textit{JWST} \textbf{cite} will provide observations in both the near-IR (600--5300~nm, R=2700) and mid-IR (4900--28\,800~nm, R$\sim$1550--3250) regions without contamination from our atmosphere.

>>>>

\subsection{Future implementation}
\label{subsec:future}
\subsubsection{High resolution instrumentation}
\label{subsubsec:highres}
The future of high resolution near- and mid- IR spectrographs is looking bright, with many new ground- and space-based instruments currently being developed. Notable examples include CARMENES (550--1710~nm, R=82\,000) which is now operational~\citep{quirrenbach_carmenes_2014}, while SPIRou (980--2350~nm, R=73\,500)~\citep{artigau_spirou_2014} and NIRPS (970--1810~nm, R=100\,000)~\citep{bouchy_nearinfrared_2017} are still being assembled and installed. The eagerly awaited \textit{JWST} \citep{gardner_james_2006} will provide observations in both the near-IR (600--5300~nm, R=2700) and mid-IR (4900--28\,800~nm, R$\sim$1550--3250) regions without contamination from our atmosphere.
